Presentasjon OPX Fiffig tittel

### 2022-08-01 Presentasjon/presentasjon.Rmd
Endret navn på bildefil kpi

## <br> Introduction | OPX and their goal
- A startup developing solutions for socially responsible investment strategies
- The goal is to increase cash flow to charitable purposes 
- Donors' trust in NGOs' financial performance and their ability to deliver results is crucial for their choice of beneficients

## <br> Introduction | How to assess financial performance?
- Data collection <br> OPX requested an automated solution to replace today's manual data collection
- Key Performance Indicators <br> OPX needed meaningful KPIs allowing to assess the relationship between assets and obligations

>>>>

## <br> OPX and their goal
- A startup developing solutions for socially responsible investment strategies
- The goal is to increase cash flow to charitable purposes 
- Donors' trust in NGOs' financial performance and their ability to deliver results is crucial for their choice of beneficients

## <br> How to assess financial performance?
- Data collection 
- Key Performance Indicators

```{r, fig.align='center'}
knitr::include_graphics("Images/kpi.png")
